---
title: "Data Scienc"
author: "Chia-Ching Chou"
date: "November 23, 2014"
output:
  html_document:
    keep_md: yes
---
Prediction Assignment Writeup

#Instroduction:

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their
behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways


#Data
The data for this project come from this source: http://groupware.les.inf.puc-rio.br/har (http://groupware.les.inf.pucrio.br/har).

#Process Data
Read trainning data and clean missing data.
```{r}
library(caret)
#read trainning data and remove missing values
inTrainData <- read.csv("pml-training.csv",na.strings=c("NA",""))
missingVals<-apply(inTrainData,2, function (x) {sum (is.na(x))})
tr_temp<-inTrainData[,missingVals==0]
trainDataFull<-tr_temp[,-(1:7)]
```

Data splitting with for traning data and cross validation (7:3).
Apply creatDataPartition function from caret package.
```{r}
inTrain<-createDataPartition(y=trainDataFull$classe,p=0.7,list=FALSE)
trainData<-trainDataFull[inTrain,]
cvData<-trainDataFull[-inTrain,]

```

#Model
apply train function from caret library
Use "rf" model
(Need to install e1071 package. I don't know why need e1071 package. It didn't install with caret package.)

```{r}
modelFit<-train(trainData[,-53],trainData$classe,method="rf",trControl=trainControl(method="oob",number=4,allowParallel=TRUE))
modelFit
```

#Validation
Cross validation.

```{r}
cv_predictions<-predict(modelFit,cvData[,-53])
confusionMatrix(cv_predictions,cvData$classe)
```

#Test
Loading testing data, and test with prediction function with modelFit variable from train() function results.
```{r}
pmlTest <- read.csv("pml-testing.csv", na.strings=c("NA",""))
testData<-pmlTest[,names(pmlTest)%in%names(trainDataFull)]
predictions<-predict(modelFit,testData)
predictions
```



